### 2020-07-01 docs/LaTex/Paper.tex
Completes docs and minor fixes

% To avoid 'underfull box' warning caused because of bibliography line-break
\usepackage{etoolbox}
\apptocmd{\thebibliography}{\raggedright}{}{}

@@

% To improve headers an footers (I'm using to set page number at right)
\usepackage{fancyhdr}
% Turn on the style
\pagestyle{fancy}
\fancyhf{} % Start with clearing everything in the header and footer
\renewcommand{\headrulewidth}{1pt} % Removes the horizontal rule in header by default
\fancyfoot[R]{\thepage} % Set the right side of the footer to be the page number
\fancyhead[R]{\rightmark}
\setlength{\headheight}{14pt}% ...at least 51.60004pt
\fancypagestyle{plain}{%
  \fancyhf{}% clear all header and footer fields
  \fancyfoot[R]{\thepage}%
  \renewcommand{\headrulewidth}{0pt}%
  \renewcommand{\footrulewidth}{0pt}%
}

@@

\begin{document}
\pagenumbering{Roman} 
\noindent % to prevent the indentation before first minipage and be able to expand minipages
\begin{minipage}[t]{.28\textwidth}
    \centering
      \begin{mdframed}[innerbottommargin=490pt, innertopmargin=40pt, linewidth=1pt]
        \includegraphics[width=\textwidth]{../pictures/Seal/marca-uex-2-color.png}
      \end{mdframed}
\end{minipage}
\hskip 30pt minus 5pt % It is a dynamic space (glue) that starts on 30pt and is 5pt shrinkable
\begin{minipage}[t]{.65\textwidth}
  \centering
  \vspace{1cm}
  \maketitle
\end{minipage}
\thispagestyle{empty}
\newpage
\begingroup
  \thispagestyle{empty}
  \null%
\endgroup
\newpage

\newpage\thispagestyle{empty}
\vspace*{\fill}
Fernando Javier Álvarez Franco, profesor del Departamento de Ingeniería Eléctrica, Electrónica y Automática de la Universidad de Extremadura.

@@

\newpage\thispagestyle{empty}
\vspace*{.5cm}

\newpage
\pagestyle{empty}\tableofcontents\clearpage\pagestyle{fancy} % set the pagestyle as empty for all toc pages

\newpage\thispagestyle{plain}\setcounter{page}{1}
\pagenumbering{arabic}% Arabic page numbers (and reset to 1)
\phantomsection\section*{Resumen}
Este documento proporciona una descripción detallada del proyecto, el cual está centrado en la investigación de posibles alternativas de bajo coste para sistemas de dendrometría inalámbricos. Actualmente existen una amplia gama de sistemas profesionales en el mercado, sin embargo debido a su elevado coste, este proyecto pretende abordar la reducción en el mismo, incrementando la versatilidad, accesibilidad y escalabilidad de este tipo de sistemas.

@@

\newpage
\section{Introduction}\thispagestyle{plain}
This project arises itself from a direct interaction with professionals inside forestry sector. The original idea was to give technical coverage for particular necessities which professionals in this sector had to face off with. At this point is easy to notice this solution will need to be a distributed solution, due high samples dispersion. As indicated, there are even remote techniques to predict this sample density/dispersion using remote methods which predicts between $157$-$170$ individuals per hectare\cite{ForestStandVol} (depending on the used model).

@@

\newpage\thispagestyle{plain}
\section{System Architecture}
A simple block diagram is shown in figure \ref{fig:block_diagram}, this diagram intends to emphasize the difference between two big layers, a physical layer that should be placed ---IoT dendrometers at least--- close to the sample, and another one called abstract layer which can be deployed locally ---TTN stack is a cloud server, although.

@@

In comparison with other common telecommunication technologies, LoRa uses lower bandwidth, but it reaches longer distances; a comparative diagram shows different wireless technologies in figure \ref{fig:LoraComparison}

@@

\newpage
\section{Design}\thispagestyle{plain}
Like in the Introduction, the most proper way to present this technical description is to difference between software and hardware parts. However, is still interesting to present a simple and general diagram for whole designed solution. So as the reader can see in the figure \ref{fig:GenView} is shown the general diagram.

@@

\newpage\thispagestyle{plain}
\section{Proof of concept}
\doubt{COMPLETE}

@@

\newpage\thispagestyle{plain}
\section{Conclusions}
Finally there are a few considerations that could be done,

@@

\newpage
\phantomsection
\addcontentsline{toc}{section}{References}
\printbibliography
\end{document}

>>>>

% To avoid 'underfull box' warning caused because of bibliography line-break
% \usepackage{etoolbox}
% \apptocmd{\thebibliography}{\raggedright}{}{}

@@

% To improve headers an footers (I'm using to set page number at right)
\usepackage{fancyhdr}
% Plain style that removes headers but keeps page numbers
\fancypagestyle{plain}{%
  \fancyhf{} % Clears all header and footer fields
  \fancyfoot[R]{\thepage}%
  \renewcommand{\headrulewidth}{0pt}%
  \renewcommand{\footrulewidth}{0pt}%
}
% This style is my custom style
\fancypagestyle{myfancy}{%
	\fancyhf{} % Start with clearing everything in the header and footer
	\renewcommand{\headrulewidth}{1pt} % Makes 1pt width the horizontal rule in header by default
	\fancyfoot[R]{\thepage} % Set the right side of the footer to be the page number
	\fancyhead[R]{\rightmark}
	\setlength{\headheight}{14pt}% ...at least 51.60004pt
}
\pagestyle{myfancy} % Enables by default the custom style.

@@

\begin{document}
\pagenumbering{Roman} 
\noindent % to prevent the indentation before first minipage and be able to expand minipages
\begin{minipage}[t]{.28\textwidth}
    \centering
      \begin{mdframed}[innerbottommargin=490pt, innertopmargin=40pt, linewidth=1pt]
        \includegraphics[width=\textwidth]{../pictures/Seal/marca-uex-2-color.png}
      \end{mdframed}
\end{minipage}
\hskip 30pt minus 5pt % It is a dynamic space (glue) that starts on 30pt and is 5pt shrinkable
\begin{minipage}[t]{.65\textwidth}
  \centering
  \vspace{1cm}
  \maketitle
\end{minipage}
\thispagestyle{empty}
\newpage
\begingroup
  \thispagestyle{empty}
  \null%
\endgroup

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{empty}
\vspace*{\fill}
Fernando Javier Álvarez Franco, profesor del Departamento de Ingeniería Eléctrica, Electrónica y Automática de la Universidad de Extremadura.

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\pagestyle{empty}

\tableofcontents\cleardoublepage\pagestyle{myfancy} % set the pagestyle as empty for all toc pages

\newpage\thispagestyle{plain}\pagenumbering{arabic}% Arabic page numbers (and reset to 1)
\phantomsection\section*{Resumen}
Este documento proporciona una descripción detallada del proyecto, el cual está centrado en la investigación de posibles alternativas de bajo coste para sistemas de dendrometría inalámbricos. Actualmente existen una amplia gama de sistemas profesionales en el mercado, sin embargo debido a su elevado coste, este proyecto pretende abordar la reducción en el mismo, incrementando la versatilidad, accesibilidad y escalabilidad de este tipo de sistemas.

@@

\clearpage{\pagestyle{empty}\cleardoublepage}
\section{Introduction}\thispagestyle{plain}
This project arises itself from a direct interaction with professionals inside forestry sector. The original idea was to give technical coverage for particular necessities which professionals in this sector had to face off with. At this point is easy to notice this solution will need to be a distributed solution, due high samples dispersion. As indicated, there are even remote techniques to predict this sample density/dispersion using remote methods which predicts between $157$-$170$ individuals per hectare\cite{ForestStandVol} (depending on the used model).

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain}
\section{System Architecture}
A simple block diagram is shown in figure \ref{fig:block_diagram}, this diagram intends to emphasize the difference between two big layers, a physical layer that should be placed ---IoT dendrometers at least--- close to the sample, and another one called abstract layer which can be deployed locally ---TTN stack is a cloud server, although.

@@

In comparison with other common telecommunication technologies, LoRa uses lower bandwidth, but it reaches longer distances; a comparative diagram shows different wireless technologies in figure \ref{fig:LoraComparison}.

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain}
\section{Design}\thispagestyle{plain}
Like in the Introduction, the most proper way to present this technical description is to difference between software and hardware parts. However, is still interesting to present a simple and general diagram for whole designed solution. So as the reader can see in the figure \ref{fig:GenView} is shown the general diagram.

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain}
\section{Proof of concept}
\doubt{COMPLETE}

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\pagestyle{plain}
\section{Conclusions}
Finally there are a few considerations that could be done,

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\pagestyle{myfancy}
\phantomsection\addcontentsline{toc}{section}{References}
\printbibliography
\end{document}
